%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvlist}

%---------------------------------------------------------
  \cvlistitem
    {\href{https://github.com/jaywonchung/BERT4Rec-VAE-Pytorch}{\myuline{BERT4Rec-VAE-Pytorch}} 
    {\normalfont(\faStarO345 \faCodeFork~81)}} % Content
    {\myuline{A PyTorch framework for recommendation model training}, with abstract classes for pluggable model, dataset, and samplers. BERT4Rec and Netflix VAE models implemented.} % Detail

  \cvlistitem
    {\href{https://github.com/jaywonchung/reason}{\myuline{Reason}}
    {\normalfont(\faStarO190 \faCodeFork~5)}} % Content
    {\myuline{A shell for managing research papers, written in Rust.} Supports importing papers from file and URL, attaching markdown notes, and creating an HTML book with notes. Uses \texttt{serde} to persist data in human-readable and cloud sync-friendly format.} % Detail

  \cvlistitem
    {\href{https://github.com/SymbioticLab/Zeus}{\myuline{Zeus}}
    {\normalfont(\faStarO188 \faCodeFork~25)}} % Content
    {\myuline{A framework for deep learning energy measurement and optimization.} \textbf{PyTorch ecosystem project.} Leading a team of two to three student contributors. Integrates best practices such as full type-annotation, auto-generated source code reference, Docker, Pytest, and examples.} % Detail

  \cvlistitem
    {\href{https://github.com/jaywonchung/pegasus}{\myuline{Pegasus}}
    {\normalfont(\faStarO31 \faCodeFork~3)}} % Content
    {\myuline{An SSH command runner with a focus on simplicity, written in Rust.} Runs multiple commands asynchronously using the \texttt{tokio} runtime and streams stdout and stderr back to the user. Battle-tested through multiple research projects and benchmarking.} % Detail

%---------------------------------------------------------
\end{cvlist}

\vspace{-5mm}

\begin{cvparagraph}
\textit{Number of stars and forks are up-to-date as of August 14th, 2024.}
\end{cvparagraph}
