%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Software Platform Lab} % Organization
    {SNU, South Korea} % Location
    {Apr 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing \textit{Crane}, an elastic GPU cluster manager}
        \item {Working with Professor Byung-Gon Chun.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Senior Project} % Job title
    {Virtual Machine and Optimization Lab} % Organization
    {SNU, South Korea} % Location
    {Dec 2019 - Jun 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Distributed DNN inference, Mobile Computing}
        \item {Worked with Professor Soo-Mook Moon on developing distributed DNN inferences schemes.}
        \item {Proposed a distributed video DNN inference scheme that drastically reduces network traffic by exploiting intermittent knowledge distillation.}
        \item {Implemented the scheme with PyTorch and OpenMPI with an NVIDIA Jetson Nano embedded board as the client and conducted evaluation.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Computer Vision Lab} % Organization
    {SNU, South Korea} % Location
    {Jun 2019 - Dec 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Meta-learning, Few-shot Classification}
        \item {Conducted research on better meta-initialization points for Model-Agnostic Meta-Learning (MAML) using an LSTM-based neural memory.}
        \item {Conducted research on generating task-aware class embeddings to augment feature maps of MAML by formulating a convex program (DPP).}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Lab of Imaging Science and Technology} % Organization
    {SNU, South Korea} % Location
    {Jun 2019 - Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Quantitative Susceptibility Mapping (QSM), Deep Learning}
        \item {Worked with Professor Jongho Lee and submitted our solution to the QSM challenge held by the 5th International Workshop on MRI Phase Contrast and QSM.}
        \item {Designed, implemented, and trained a U-Net variant on in-vivo brain MRI field images and their COSMOS results.}
      \end{cvitems}
    }
%---------------------------------------------------------
%   \cventry
%     {Intern Computer Programmer} % Job title
%     {LCPtracker, inc} % Organization
%     {E Chapman Ave, Orange,CA 92866} % Location
%     {Jun 2015 - Aug 2015} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item{Implemented a mobile Xamarin application for labor compliance.}
%         \item {Implemented MVVM patterns and repository patterns for an Sqlite backend}
%         \item {Implemented a way to consume API request from an ASP.NET server.}
%       \end{cvitems}
%     }

\end{cventries}
